Macroscopic Salt Rejection through Electrostatically Gated Porous Graphene

### 2019-01-09 paper/paper.tex
Change equation 1

First, the control experiments were carried out by measuring the ionic
diffusion of seven salt species, including KCl, NaCl, LiCl,
K$_{2}$SO$_{4}$, MgSO$_{4}$, CaCl$_{2}$ and K$_{3}$[Fe(CN)$_{6}$],
through the bare PCTE membrane at $c_{0}$ = 0.1 mM. As the diffusive
flux is comparably small, the conductivity increases linearly with time in the LCR
(e.g. \Fig{} \ref{fig:2}a) within the measurement duration (1 h),
suggesting the concentration gradient across the membrane remains 
constant. The diffusive fluxes (blue bars in \Fig{} \ref{fig:2}b) of different salts were
obtained by converting the conductivity-time profiles using
calibration curves (Supplementary Section S2). The theoretical diffusive fluxes through PCTE are obtained based on the assumption that the
membrane consists of cylindrical pores with uniform diameter and a low
tortuosity $\tau$ of $\sim{}$1.2 \cite{O_Hern_2012}:

  \begin{equation}
    \label{eq:j-pcte}
    \boldsymbol{J}_{\mathrm{PCTE}} = \frac{\pi a^{2} N_{\mathrm{p}} D \Delta c}{\delta \tau}
  \end{equation}

where $a$ is the PCTE pore radius, $N_{\mathrm{p}}$ is numbers of pore
per area, $D$ is the salt diffusivity (average of cation and anion diffusivity), $\Delta c$ is the bulk
concentration difference between two reservoirs, i.e.,
$\Delta c \sim c_{0}$ and $\delta$ is the thickness of the PCTE membrane.
 By using the salt diffusivity values (Supplementary Table S1), the
calculated diffusive fluxes (red bars in \Fig{} \ref{fig:2}b) show
reasonable agreement with the experimental values.

>>>>

First, the control experiments were carried out by measuring the ionic
diffusion of seven salt species, including KCl, NaCl, LiCl,
K$_{2}$SO$_{4}$, MgSO$_{4}$, CaCl$_{2}$ and K$_{3}$[Fe(CN)$_{6}$],
through the bare PCTE membrane at $c_{0}$ = 0.1 mM. As the diffusive
flux is comparably small, the conductivity increases linearly with time in the LCR
(e.g. \Fig{} \ref{fig:2}a) within the measurement duration (1 h),
suggesting the concentration gradient across the membrane remains 
constant. The diffusive fluxes (blue bars in \Fig{} \ref{fig:2}b) of different salts were
obtained by converting the conductivity-time profiles using
calibration curves (Supplementary Section S2). The theoretical diffusive fluxes through PCTE are obtained based on the assumption that the
membrane consists of cylindrical pores with uniform diameter and a low
tortuosity $\tau$ of $\sim{}$1.2 \cite{O_Hern_2012}:
\begin{equation}
  \label{eq:j-pcte}
  \boldsymbol{J}_{\mathrm{PCTE}} = \frac{\pi r_{\mathrm{PCTE}}^{2} N_{\mathrm{p}} D_{\mathrm{\pm}} \Delta c}{L \tau}
\end{equation}

where $r_{\mathrm{PCTE}}$ is the PCTE pore radius, $N_{\mathrm{p}}$ is
numbers of pore per area, $D_{\mathrm{\pm}}$ is the salt diffusivity
(average of cation and anion diffusivity), $\Delta c$ is the bulk
concentration difference between two reservoirs, i.e.,
$\Delta c \sim c_{0}$ and $L$ is the thickness of the PCTE membrane.
By using the salt diffusivity values (Supplementary Table S1), the
calculated diffusive fluxes (red bars in \Fig{} \ref{fig:2}b) show
reasonable agreement with the experimental values.
